{\bf Intrusion Detection using Parzen-Windows on Provenance Graph Statistics}

### 2013-12-10 writeup/paper-final.tex
edits

\begin{abstract}
Security rests on being able to identify potentially malicious behavior.
One way to identify malicious behavior is to compare system behavior to known normal behavior.
Intrusions on a system leave typically leave behind digital artifacts, and we hypothesize
that we can detect intrusions on a system by identifying anomalies the artifacts' provenance, the lineage of how
the artifact came to be in its present state.
We present an intrusion detection approach to find these anomalies by analyzing centrality metrics
on provenance graphs. We use a Parzen-Window approach \cite{parzen} on various provenance graph centrality metrics \cite{clustering}
to determine probability density estimates of normal behavior, and we use these density estimates to 
determine if an intrusion occurred. We used this approach to analyze {\em user-to-remote} (u2r) intrusions 
from the 1998 DARPA Intrusion Detection data sets \cite{darpa} and 
achieved up to *TODO true positive rate for intrusions* accuracy in detecting
intrusions with only *TODO false positive rate for intrusions* accuracy. We also present future work
to extend our intrusion model to an online intrusion detection system.

>>>>

\begin{abstract}
Security rests on being able to identify potentially malicious behavior.
One way to identify malicious behavior is to compare system behavior to known normal behavior.
Intrusions on a system typically leave behind digital artifacts, and we hypothesize
that we can detect intrusions on a system by identifying anomalies in the artifacts' {\em provenance}, or the lineage of how
the artifact came to be in its present state.
We present an intrusion detection approach to find these anomalies by analyzing provenance graphs statistics. We use a Parzen-Window approach \cite{parzen} on various provenance graph statistics \cite{clustering}
to determine probability density estimates of normal behavior, and we use these density estimates to 
determine if an intrusion occurred. We used this approach to analyze {\em user-to-remote} (u2r) intrusions 
from the 1998 DARPA Intrusion Detection data sets \cite{darpa} and 
achieved up to *TODO true positive rate for intrusions* accuracy in detecting
intrusions with only *TODO false positive rate for intrusions* accuracy. We also present future work
to extend our intrusion model to an online intrusion detection system.
